Expanding the scope of experimental archaeology using the Perception-Process-Product conceptual framework

### 2023-07-22 manuscript/manuscript.Rmd
minor fix

I would like to thank Dietrich Stout for his helpful comments on earlier drafts of this article. I am also grateful for my collaborators who help me turn this idea into reality: Russell Cutts (Oxford College of Emory University), Nada Khreisheh (The Ancient Technology Centre), Justin Pargeter (New York University), Ron Shimelmitz (University of Haifa), and particularly Mark Moore (University of New England). This study was supported by a research grant from the Leakey Foundation titled "Inferring skill reproduction from stone artifacts: A middle‐range approach"

>>>>

I would like to thank Dietrich Stout for his helpful comments on earlier drafts of this article. I am also grateful for my collaborators who help me turn this idea into reality: Russell Cutts (Oxford College of Emory University), Nada Khreisheh (The Ancient Technology Centre), Justin Pargeter (New York University), Ron Shimelmitz (University of Haifa), and particularly Mark Moore (University of New England). This study was supported by a research grant from the Leakey Foundation titled "Inferring skill reproduction from stone artifacts: A middle‐range approach."
